scikit-image, a Python library for 2D and 3D image processing

### 2016-08-16 skimage_tomo.tex
Some progress on image capabilities section

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={emmanuelle.gouillart@saint-gobain.com}   % email address
]{\fnm{Emmanuelle} \snm{Gouillart}}
\author[
   addressref={aff2},
   %email={}
]{\fnm{Juan} \snm{Nunez-Iglesias}}
\author[
   addressref={aff3},
   email={stefanv@berkeley.edu}
]{\fnm{Stéfan} \snm{van der Walt}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Surface du Verre et Interfaces, UMR 125 CNRS/Saint-Gobain}, % university, etc                     %
  \postcode{93303}                                % post or zip code
  \city{Aubervilliers},                              % city
  \cny{France}                                    % country
}
\address[id=aff2]{%
  \orgname{Victorian Life Sciences Computation Initiative, University of Melbourne},
  %\street{700 Swanston St},
  %\postcode{3053}
  \city{Carlton, VIC},
  \cny{Australia}
}
\address[id=aff3]{%
  \orgname{Division of Applied Mathematics, Stellenbosch University},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  \city{Stellenbosch},
  \cny{South Africa}
}

@@

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ~\citep{Abramoff2004, Schneider2012}
and its distribution Fiji~\citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid
community~\citep{Schindelin2015}. For 3-D images, commercial tools such
as Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- hence
limiting the programming task and the risk of bugs. Matlab (TM) and its
image processing toolbox are popular in the academic community of
computer vision and image processing. The Python language is widely used
in the scientific world and in synchrotron facilities. As a
general-purpose language, Python is used in synchrotrons to control
device servers~\citep{pytango}, to reconstruct tomography volumes from
radiographs~\citep{Gursoy2014, Mirone2014}, and in data
processing packages for macromolecular cristallography~\citep{Adams2010},
azimuthal integration of diffraction data~\citep{Ashiotis2015} or
fluorescence analysis~\citep{pymca}.

\texttt{scikit-image}~\citep{Vanderwalt2014} is a general-purpose image
processing library for the Python language, and a component of the ecosystem of
Python scientific modules commonly known as Scientific
Python~\citep{Oliphant2007}. Like the rest of the ecosystem,
\texttt{scikit-image} is released under a permissive open-source license and is
available free of charge. Most of \texttt{scikit-image} is compatible with both 2-D and
3-D images, so that it can be used for a large number of imaging modalities,
such as microscopy, radiography or tomography. In this article, we explain how
\texttt{scikit-image} can be used for processing data acquired in synchrotron
imaging experiments, with a strong focus on microtomography 3-D images. This
article does not intend to be a pedagogical tutorial on \texttt{scikit-image}
for X-ray imaging, but rather to explain the rationale behind the package, and
provide various examples of its capabilities.

@@

Images are manipulated as numerical arrays of uniform
data type, a format that guarantees a fast access to the computer memory. The
n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
\texttt{NumPy} module~\citep{Vanderwalt2011}.

In image processing, one of the first tasks is therefore to generate
\texttt{NumPy} arrays, which is often done by reading data from files. We
read one 2-D image from a file and display it with the following lines of code:

@@

The benefits of \texttt{scikit-image} for image processing come not only
from the features of the package alone, but also from the rich
environment of Scientific Python~\citep{Oliphant2007, Perez2011}.
Fig.~\ref{fig:ecosystem} illustrates how several components of this
ecosystem combine into a sophisticated image processing workflow.

@@

While several interpreters are available to execute interactively Python
instructions and scripts, the most popular one in the scientific world is
the IPython interpreter~\citep{Perez2007, Rossant2015}. IPython is an
advanced interpreter, which integrates syntax highlighting, text auto-completion,
a debugger,
introspection and profiling methods, and online help. Several
Integrated Development Environments (IDEs) include IPython,
together with other components such as a text editor. Notable examples
include Spyder (Fig.~\ref{fig:spyder}), PyCharm, and Visual Studio Code.

@@

The Jupyter notebook~\citep{Kluyver2016} is a web application that grew
from the IPython project. Jupyter notebooks provide an interactive development
environment within a web browser, where live code can be enriched
by explanatory text, equations and visualizations (FIGURE).
(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)

@@

Visualizing images is an important component of the image processing
workflow, in order to verify the final result and to adjust the
parameters of intermediate processing operations.
\texttt{matplotlib}~\citep{Hunter2007} is the most popular 2D plotting
library of the Python ecosystem. It can be used to visualize 2D data such
as color or grayscale images, and 1D data such as contour lines, outlines
of segmented regions, histograms of gray levels, etc. Although
\texttt{matplotlib} has simple 3D plotting capabilities, we
recommend using the \texttt{mayavi} module~\citep{Ramachandran2011}
for applications requiring advanced 3D visualization, such as tomography. 
\texttt{mayavi} is based on the VTK toolkit. It exposes a simple API for
visualizing data passed as \texttt{numpy} arrays. For more advanced
visualizations, a large majority of VTK capabilities can be accessed
thanks to a pipeline API.
\texttt{mayavi} offers a good trade-off between simplicity of use for
common operations, and more advanced possibilities, including responsive
visualizations.

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
\caption{\csentence{Sample figure title.}
      A short description of the figure content
      should go here.}
\end{figure*}

>>>>

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={emmanuelle.gouillart@saint-gobain.com}   % email address
]{\fnm{Emmanuelle} \snm{Gouillart}}
\author[
   addressref={aff2},
   %email={}
]{\fnm{Juan} \snm{Nunez-Iglesias}}
\author[
   addressref={aff3},
   email={stefanv@berkeley.edu}
]{\fnm{Stéfan} \snm{Van der Walt}}

@@

\address[id=aff1]{%                           % unique id
  \orgname{Surface du Verre et Interfaces, UMR 125 CNRS/Saint-Gobain}, % university, etc                     %
  \postcode{93303}                                % post or zip code
  \city{Aubervilliers},                              % city
  \cny{France}                                    % country
}
\address[id=aff2]{%
  \orgname{Life Sciences Computation Centre, University of Melbourne},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  \city{Melbourne},
  \cny{Australia}
}
\address[id=aff3]{%
  \orgname{Division of Applied Mathematics, Stellenbosch University},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  \city{Stellenbosch},
  \cny{South Africa}
}

@@

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ~\citep{Abramoff2004, Schneider2012}
and its distribution Fiji~\citep{Schindelin2012} is a popular tool for
2-D and 3-D images, thanks to its intuitive menus and graphical tools,
and the wealth of plugins contributed by a vivid
community~\citep{Schindelin2015}. For 3-D images, commercial tools such
as Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- hence
limiting the programming task and the risk of bugs. Matlab (TM) and its
image processing toolbox are popular in the academic community of
computer vision and image processing. The Python language is widely used
in the scientific world and in synchrotron facilitiies. As a
general-purpose language, Python is used in synchrotrons for controlling
device servers~\citep{pytango}, reconstructing tomography volumes from
radiographies~\citep{Gursoy2014, Mirone2014}, and various data
processing packages for macromolecular cristallography~\citep{Adams2010},
azimuthal integration of diffraction data~\citep{Ashiotis2015} or
fluorescence analysis~\citep{pymca}.

\texttt{scikit-image}~\citep{Vanderwalt2014} is a general-purpose image
processing library for the Python language, and a component of the ecosystem of
Python scientific modules commonly known as Scientific
Python~\citep{Oliphant2007}. Like the rest of the ecosystem,
\texttt{scikit-image} is released under a permissive open-source license and is
available free of charge. \texttt{scikit-image} is compatible with both 2-D and
3-D images, so that it can be used for a large number of imaging modalities,
such as microscopy, radiography or tomography. In this article, we explain how
\texttt{scikit-image} can be used for processing data acquired in synchrotron
imaging experiments, with a strong focus on microtomography 3-D images. This
article does not intend to be a pedagogical tutorial on \texttt{scikit-image}
for X-ray imaging, but rather to explain the rationale behind the package, and
what can be done with \texttt{scikit-image}.

@@

Image are manipulated as numerical arrays of uniform
data type, a format that guarantees a fast access to the computer memory. The
n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
\texttt{NumPy} module~\citep{Vanderwalt2011}.

In image processing, one of the first tasks is therefore to generate
\texttt{NumPy} arrays, which is often done by reading data from files. Let us
read one 2-D image from a file and display it with the following lines of code:

@@

The benefits of \texttt{scikit-image} for image processing come not only
from the features of the package alone, but also from the rich
environment of Scientific Python~\citep{Oliphant2007, Perez2011}.
Fig.~\ref{fig:ecosystem} illustrates how several components of this
ecosystem are used for a typical image processing workflow.

@@

While several interpreters are available to execute interactively Python
instructions and scripts, the most popular one in the scientific world is
the IPython interpreter~\citep{Perez2007, Rossant2015}. IPython is an
advanced interpreter, which integrates for example a debugger,
introspection and profiling methods, and online help. Several IDEs
(Integrated Development Environment) integrate the IPython interpreter,
together with other components such as a text editor. For example, Spyder 
is a popular IDE (see Fig.~\ref{fig:spyder}).

@@

The Jupyter notebook~\citep{Kluyver2016} is a web application which has
grown from the IPython project, although the two projects have now
diverged. Jupyter notebooks provide an interactive development
environment within an Internet browser, where live code can be enriched
by explanatory text, equations and visualizations (figure or not??).

@@

Visualizing images is an important component of the image processing
workflow, in order to verify the final result and to adjust the
parameters of intermediate processing operations.
\texttt{matplotlib}~\citep{Hunter2007} is the most popular 2D plotting
library of the Python ecosystem. It can be used to visualize 2D data such
as color or grayscale images, and 1D data such as contour lines, outlines
of segmented regions, histograms of gray levels, etc. Although
\texttt{matplotlib} has simple 3D plotting capabilities, it is
recommended to use the \texttt{mayavi} module~\citep{Ramachandran2011}
for applications requiring advanced 3D visualization, such as tomography. 
\texttt{mayavi} is based on the VTK toolkit. It exposes a simple API for
visualizing data passed as \texttt{numpy} arrays. For more advanced
visualizations, a large majority of VTK capabilities can be accessed
thanks to a pipeline API. A visualization pipeline can be designed either
using the pipeline API, or graphically in the pipeline window.
\texttt{mayavi} offers a good trade-off between simplicity of use for
common operations, and more advanced possibilities, including responsive
visualizations.

@@

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
\caption{\csentence{Sample figure title.}
      A short description of the figure content
  should go here. \label{fig:tomo_gallery}}
\end{figure*}

\texttt{scikit-image} offers all the classical operations of image
processing, such as exposure and color adjustment, filtering,
segmentation, features extraction, geometric transformations or
measurements of region characteristics. For these
different categories, the package includes both standard generic
operations and more advanced algorithms. A sample of
\texttt{scikit-image} capabilities is given in
Fig.~\ref{fig:tomo_gallery}.

Tomographic images often suffer from artifacts or poor signal-to-noise
ratio. Several denoising filters are available for image restoration,
from general-purpose filters such as median and bilateral filters, to more
specific filters. Total-variation denoising~\citep{Chambolle2004,
Getreuer2012} is well-suited to restore
piecewise-constant images, such as images with a small number of phases
encountered in materials science~\citep{Bouttes2015}. Conversely, images
with a fine-grained texture are better preserved with non-local means
denoising~\citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
